Formalization of Network Flow Algorithms

### 2017-02-28 paper/root.tex
Merged all diagrams into one Legend, added titles

  \begin{figure}[!h]
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {0,1000,...,5000},
        ytick = {0.01,0.1,1,10},
        xticklabels = {$1000$, $2000$, $3000$, $4000$, $5000$},
        yticklabels = {$0.01$,$0.1$,$1$,$10$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.515,0.24)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting
      \addplot table {
        1000 .024   
        1500 .098  
        2000 .211  
        2500 .693  
        3000 2.014 
        3500 3.153 
        4000 3.679 
        4500 8.364 
        5000 10.328 
        5500 11.749    
      }; \addlegendentry{edka-SML, sparse};

      \addplot table {
        1000 .024   
        1500 .054   
        2000 .103  
        2500 .399  
        3000 .719  
        3500 1.362 
        4000 2.036 
        4500 3.334 
        5000 4.785 
        5500 6.079     
      }; \addlegendentry{edka-Java, sparse};

      \addplot table {
        1000 .005   
        1500 .013  
        2000 .024  
        2500 .037  
        3000 .066 
        3500 .077 
        4000 .096 
        4500 .146 
        5000 .194 
        5500 .192    
      }; \addlegendentry{prpu-SML, sparse};
    %end data for plotting
    \end{axis}
  \end{tikzpicture}
%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {0,1000,1100,...,1400},
        ytick = {1,4,...,16},
        xticklabels = {$1000$, $1100$, $1200$, $1300$, $1400$}, 
        yticklabels = {$1$,$4$,$8$,$12$,$16$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.53,0.6)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting
      \addplot table {
        1000	2.794
        1050	2.9
        1100	4.405
        1150	4.435
        1200	5.232
        1250	6.029
        1300	7.699
        1350	8.91
        1400	7.225
        1450	10.042 
      }; \addlegendentry{edka-SML, dense};

      \addplot table {
        1000	3.982
        1050	4.463
        1100	5.278
        1150	6.27
        1200	6.939
        1250	7.953
        1300	9.392
        1350	10.317
        1400	14.71
        1450	13.11  
      }; \addlegendentry{edka-Java, dense};

      \addplot table {
        1000	0.074
        1050	0.059
        1100	0.068
        1150	0.075
        1200	0.102
        1250	0.085
        1300	0.096
        1350	0.103
        1400	0.088
        1450	0.114  
      }; \addlegendentry{prpu-SML, dense};
    \end{axis}
  \end{tikzpicture}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {3000, 6000, 10500, 13500, 16500},
        ytick = {0.1,1,10,50,100},
        xticklabels = {$3k$, $6k$, $10k$, $13k$, $16k$},
        yticklabels = {$\text{\ \,}0.1$,$1$,$10$,$50$,$100$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.53,0.24)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting

      \addplot table {
        3000	1.185
        4500	3.524
        6000	6.457
        7500	11.509
        9000	17.529
        10500	26.185
        12000	36.828
        13500	48.614
        15000	86.449
        16500	89.661
      }; \addlegendentry{prpu-SML, wash};

      \addplot table {
        3000	0.906
        4500	2.708
        6000	5.083
        7500	8.792
        9000	12.951
        10500	19.075
        12000	27.466
        13500	35.964
        15000	61.839
        16500	67.039
      }; \addlegendentry{prpu-C++, wash};

      \addplot table {
        3000	0.006
        4500	0.015
        6000	0.029
        7500	0.042
        9000	0.063
        10500	0.084
        12000	0.115
        13500	0.144
        15000	0.183
        16500	0.223
      }; \addlegendentry{prpu-C, wash};
    %end data for plotting
    \end{axis}
  \end{tikzpicture}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {0,1000,1100,...,1400},
        ytick = {0.01, 0.1, 0.2, 0.5, 1},
        xticklabels = {$1000$, $1100$, $1200$, $1300$, $1400$}, 
        yticklabels = {$0.01$, $0.1$,$0.2$,$0.5$,$1$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.52,0.24)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting
      \addplot table {
        1000	0.141
        1050	0.202
        1100	0.157
        1150	0.273
        1200	0.24
        1250	0.408
        1300	0.465
        1350	1.416
        1400	0.657
        1450	0.806
      }; \addlegendentry{prpu-SML, acnet};

      \addplot table {
        1000	0.121
        1050	0.17
        1100	0.123
        1150	0.216
        1200	0.197
        1250	0.237
        1300	0.298
        1350	0.621
        1400	0.399
        1450	0.486
      }; \addlegendentry{prpu-C++, acnet};

      \addplot table {
        1000	0.056
        1050	0.09
        1100	0.069
        1150	0.106
        1200	0.09
        1250	0.152
        1300	0.163
        1350	0.176
        1400	0.223
        1450	0.209
      }; \addlegendentry{prpu-C, acnet};
    \end{axis}
  \end{tikzpicture}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {16000,19000,23000,27000,30000},
        ytick = {0.1,1,5,10,25},
        xticklabels = {$16k$, $19k$, $23k$, $27k$, $30k$}, 
        yticklabels = {$\text{\ \,}0.1$, $1$,$5$,$10$,$25$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.49,0.6)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting
      \addplot table {
        16000	3.602
        17600	4.223
        19200	4.839
        20800	8.201
        22400	8.273
        24000	13.426
        25600	10.089
        27200	15.889
        28800	16.431
        30400	21.437
      }; \addlegendentry{prpu-SML, genrmf};

      \addplot table {
        16000	4.51
        17600	4.804
        19200	5.899
        20800	8.052
        22400	8.448
        24000	11.555
        25600	8.878
        27200	13.999
        28800	12.99
        30400	13.791
      }; \addlegendentry{prpu-C++, genrmf};

      \addplot table {
        16000	0.009
        17600	0.012
        19200	0.015
        20800	0.021
        22400	0.021
        24000	0.019
        25600	0.023
        27200	0.028
        28800	0.026
        30400	0.026
      }; \addlegendentry{prpu-C, genrmf};
    \end{axis}
  \end{tikzpicture}
  \caption{Benchmark of different implementations. The x-axis shows the number of nodes, the y axis the execution time in seconds.}\label{fig:benchmark}
  \end{figure}

>>>>

\begin{figure}[!h]    
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{groupplot}[
        group style={
            group size=2 by 3,
            vertical sep=1.5cm,
        }
    ]

    \nextgroupplot[
        title={Random Sparse Graphs},
        title style={yshift=-2ex},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
        xtick = {0,1000,...,5000},
        ytick = {0.01,0.1,1,10},
        xticklabels = {$1000$, $2000$, $3000$, $4000$, $5000$},
        yticklabels = {$0.01$,$0.1$,$1$,$10$},
        smooth,
        cycle list name = black white,
        legend cell align={left},
        legend to name=grouplegend
    ]
    % legend information
      \addlegendimage{fill=gray, mark=square}
      \addlegendimage{fill=gray, mark=square*}
      \addlegendimage{fill=gray, mark=*}
      \addlegendimage{fill=gray, mark=o}
      \addlegendimage{fill=gray, mark=otimes*}
      \addlegendentry{Edmonds-Karp, SML}
      \addlegendentry{FIFO push-relabel, SML}
      \addlegendentry{Edmonds-Karp, Java}
      \addlegendentry{FIFO push-relabel, C++}
      \addlegendentry{FIFO push-relabel, C}
    % end legend information

		%start data for plotting
		  \addplot+[mark=square] table {
		    1000 .024   
		    1500 .098  
		    2000 .211  
		    2500 .693  
		    3000 2.014 
		    3500 3.153 
		    4000 3.679 
		    4500 8.364 
		    5000 10.328 
		    5500 11.749    
		  }; %Sparse, Edka, SML

		  \addplot+[mark=*] table {
		    1000 .024   
		    1500 .054   
		    2000 .103  
		    2500 .399  
		    3000 .719  
		    3500 1.362 
		    4000 2.036 
		    4500 3.334 
		    5000 4.785 
		    5500 6.079     
		  }; %Sparse, Edka, Java

		  \addplot+[mark=square*] table {
		    1000 .005   
		    1500 .013  
		    2000 .024  
		    2500 .037  
		    3000 .066 
		    3500 .077 
		    4000 .096 
		    4500 .146 
		    5000 .194 
		    5500 .192    
		  }; %Sparse, Prpu, SML 
		%end data for plotting

	\nextgroupplot[
    	title={Random Dense Graphs},
    	title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {0,1000,1100,...,1400},
      ytick = {1,4,...,16},
      xticklabels = {$1000$, $1100$, $1200$, $1300$, $1400$}, 
      yticklabels = {$1$,$4$,$8$,$12$,$16$}, 
      smooth,
      cycle list name = black white
	]

		%start data for plotting 
		  \addplot+[mark=square] table {
		    1000	2.794
		    1050	2.9
		    1100	4.405
		    1150	4.435
		    1200	5.232
		    1250	6.029
		    1300	7.699
		    1350	8.91
		    1400	7.225
		    1450	10.042 
		  }; %Dense, Edka, SML

		  \addplot+[mark=*] table {
		    1000	3.982
		    1050	4.463
		    1100	5.278
		    1150	6.27
		    1200	6.939
		    1250	7.953
		    1300	9.392
		    1350	10.317
		    1400	14.71
		    1450	13.11  
		  }; %Dense, Edka, Java

		  \addplot+[mark=square*] table {
		    1000	0.074
		    1050	0.059
		    1100	0.068
		    1150	0.075
		    1200	0.102
		    1250	0.085
		    1300	0.096
		    1350	0.103
		    1400	0.088
		    1450	0.114  
		  }; %Dense, Prpu, SML  
		%end data for plotting

	\nextgroupplot[
      title={Goldberg's Bad Case (Washington)},
      title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {3000, 6000, 10500, 13500, 16500},
      ytick = {0.1,1,10,50,100},
      xticklabels = {$3k$, $6k$, $10k$, $13k$, $16k$},
      yticklabels = {$0.1$,$1$,$10$,$50$,$100$}, 
      smooth,
      cycle list name = black white
	]

    %start data for plotting
      \addplot+[mark=square*] table {
        3000	1.185
        4500	3.524
        6000	6.457
        7500	11.509
        9000	17.529
        10500	26.185
        12000	36.828
        13500	48.614
        15000	86.449
        16500	89.661
      }; %WASH, Prpu, SML

      \addplot+[mark=o] table {
        3000	0.906
        4500	2.708
        6000	5.083
        7500	8.792
        9000	12.951
        10500	19.075
        12000	27.466
        13500	35.964
        15000	61.839
        16500	67.039
      }; %WASH, Prpu, C++

      \addplot+[mark=otimes*] table {
        3000	0.006
        4500	0.015
        6000	0.029
        7500	0.042
        9000	0.063
        10500	0.084
        12000	0.115
        13500	0.144
        15000	0.183
        16500	0.223
      }; %WASH, Prpu, C

	\nextgroupplot[
      title={Fully Dense Acyclic Networks (Waissi)},
      title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {0,1000,1100,...,1400},
      ytick = {0.01, 0.1, 0.2, 0.5, 1},
      xticklabels = {$1000$, $1100$, $1200$, $1300$, $1400$}, 
      yticklabels = {$0.01$, $0.1$,$0.2$,$0.5$,$1$}, 
      smooth,
      cycle list name = black white
	]

    %start data for plotting 
      \addplot+[mark=square*] table {
        1000	0.141
        1050	0.202
        1100	0.157
        1150	0.273
        1200	0.24
        1250	0.408
        1300	0.465
        1350	1.416
        1400	0.657
        1450	0.806
      }; %ACNET, Prpu, SML

      \addplot+[mark=o] table {
        1000	0.121
        1050	0.17
        1100	0.123
        1150	0.216
        1200	0.197
        1250	0.237
        1300	0.298
        1350	0.621
        1400	0.399
        1450	0.486
      }; %ACNET, Prpu, C++

      \addplot+[mark=otimes*] table {
        1000	0.056
        1050	0.09
        1100	0.069
        1150	0.106
        1200	0.09
        1250	0.152
        1300	0.163
        1350	0.176
        1400	0.223
        1450	0.209
      }; %ACNET, Prpu, C

	\nextgroupplot[
      title={RMFGEN Networks (Goldfarb et. al)},
      title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {16000,19000,23000,27000,30000},
      ytick = {0.1,1,5,10,25},
      xticklabels = {$16k$, $19k$, $23k$, $27k$, $30k$}, 
      yticklabels = {$0.1$, $1$,$5$,$10$,$25$}, 
      smooth,
      cycle list name = black white
	]

    %start data for plotting
      \addplot+[mark=square*] table {
        16000	3.602
        17600	4.223
        19200	4.839
        20800	8.201
        22400	8.273
        24000	13.426
        25600	10.089
        27200	15.889
        28800	16.431
        30400	21.437
      }; %RPFGEN, Prpu, SML

      \addplot+[mark=o] table {
        16000	4.51
        17600	4.804
        19200	5.899
        20800	8.052
        22400	8.448
        24000	11.555
        25600	8.878
        27200	13.999
        28800	12.99
        30400	13.791
      }; %RPFGEN, Prpu, C++

      \addplot+[mark=otimes*] table {
        16000	0.009
        17600	0.012
        19200	0.015
        20800	0.021
        22400	0.021
        24000	0.019
        25600	0.023
        27200	0.028
        28800	0.026
        30400	0.026
      }; %RPFGEN, Prpu, C  
    \end{groupplot}

    \node at (group c1r3.east) [anchor=west, xshift= 1cm] {\ref{grouplegend}};
  \end{tikzpicture}
\caption{Benchmark of different implementations. The x-axis shows the number of nodes, the y axis the execution time in seconds.}\label{fig:benchmark}
\end{figure}
